---
title: "CrimeMarkdown"
author: "Cyrus Tadjiki"
date: "2/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "C:/Users/cyrus/Downloads/EC 419/Crime Data")
getwd()
```


# Managing Crime Data from NIBRS
#load packages
```{r, warning=FALSE}
library(pacman)
p_load(tidyverse, rvest, lubridate, janitor, 
       data.table, readr, readxl, dplyr, skimr, 
       broom, tidyr, stringr, stats)
```


# Gathering data this takes 3 minutes to run
```{r, echo=FALSE}
# setwd("C:/Users/cyrus/Downloads/EC 419/Crime Data")
#pull example files
NIBRS_incident <- read_csv("Crime_Data_2020/AR/NIBRS_incident.csv")
NIBRS_VICTIM <- read_csv("Crime_Data_2020/AR/NIBRS_VICTIM.csv")
agencies <- read_csv("Crime_Data_2020/AR/agencies.csv")

#make empty data set for incident data
incidents <- data.frame(matrix(ncol = 15, nrow = 0))
names(incidents) <- c("DATA_YEAR", "AGENCY_ID", "INCIDENT_ID", "NIBRS_MONTH_ID",    
                      "CARGO_THEFT_FLAG", "SUBMISSION_DATE", "INCIDENT_DATE", 
                      "REPORT_DATE_FLAG", "INCIDENT_HOUR", "CLEARED_EXCEPT_ID", 
                      "CLEARED_EXCEPT_DATE", "INCIDENT_STATUS","DATA_HOME", 
                      "ORIG_FORMAT" , "DID")

# get a list of the folders in Crime_Data_NIBRS
files <- list.files(path="CRIME_DATA_2020")

#go through each folder in Crime_Data_NIBRS and find corresponding incident 
#table to bind it to incidents data frame
for (i in files){
  NIBRS_incident <- read_csv(gsub(' ', '', paste("Crime_Data_2020/", i, "/NIBRS_incident.csv")))
  incidents <- rbind(incidents, NIBRS_incident)
}

#pull out unnecessary columns for incidents data set
incidents <- incidents[ , c("DATA_YEAR", "AGENCY_ID", "INCIDENT_ID",
                            "INCIDENT_DATE", "INCIDENT_HOUR")]

#make empty data set for victim data
victims <- data.frame(matrix(ncol = 16, nrow = 0))
names(victims) <- c("DATA_YEAR", "VICTIM_ID", "INCIDENT_ID", "VICTIM_SEQ_NUM",   
                    "VICTIM_TYPE_ID", "ASSIGNMENT_TYPE_ID", "ACTIVITY_TYPE_ID", 
                    "OUTSIDE_AGENCY_ID", "AGE_ID", "AGE_NUM", "SEX_CODE", 
                    "RACE_ID", "ETHNICITY_ID", "RESIDENT_STATUS_CODE", 
                    "AGE_RANGE_LOW_NUM", "AGE_RANGE_HIGH_NUM")  

#go through each folder and find corresponding  
for (i in files){
  NIBRS_VICTIM <- read_csv(gsub(' ', '', paste("Crime_Data_2020/", i, "/NIBRS_VICTIM.csv")))
  victims <- rbind(victims, NIBRS_VICTIM)
}


victims <- victims[ , c("VICTIM_ID", "INCIDENT_ID", 
                        "AGE_NUM", "SEX_CODE")]


agency_list <- data.frame(matrix(ncol = 59, nrow = 0))

names(agency_list) <- names(agencies)

for (i in files){
  agencies <- read_csv(gsub(' ', '', paste("Crime_Data_2020/", i, "/agencies.csv")))
  agency_list <- rbind(agency_list, agencies)
}

agency_list <- agency_list[ , c("YEARLY_AGENCY_ID", "AGENCY_ID", "STATE_NAME", "STATE_ABBR",
                                "AGENCY_TYPE_NAME", "UCR_AGENCY_NAME", "COUNTY_NAME")]

NIBRS_OFFENDER <- read_csv("Crime_Data_2020/AL/NIBRS_OFFENDER.csv")

offenders <- data.frame(matrix(ncol = 11, nrow = 0))

names(offenders) <- names(NIBRS_OFFENDER)



for (i in files){
  NIBRS_OFFENDER <- read_csv(gsub(' ', '', paste("Crime_Data_2020/", i, "/NIBRS_OFFENDER.csv")))
  offenders <- rbind(offenders, NIBRS_OFFENDER)
}

offenders <- offenders[ , c("OFFENDER_ID", "INCIDENT_ID")]

NIBRS_OFFENSE <- read_csv("Crime_Data_2020/AL/NIBRS_OFFENSE.csv")

offense <- data.frame(matrix(ncol = 8, nrow = 0))

names(offense) <- names(NIBRS_OFFENSE)

for (i in files){
  NIBRS_OFFENSE <- read_csv(gsub(' ', '', paste("Crime_Data_2020/", i, "/NIBRS_OFFENSE.csv")))
  offense <- rbind(offense, NIBRS_OFFENSE)
}

offense <- offense[ , c("OFFENSE_ID", "INCIDENT_ID", 
                        "OFFENSE_TYPE_ID", "LOCATION_ID")]

NIBRS_VICTIM_OFFENDER_REL <- read_csv("Crime_data_2020/AL/NIBRS_VICTIM_OFFENDER_REL.csv")

victim_offender_rel <- data.frame(matrix(ncol = 5, nrow = 0))

names(victim_offender_rel) <- names(NIBRS_VICTIM_OFFENDER_REL)

for (i in files){
  NIBRS_VICTIM_OFFENDER_REL <- read_csv(gsub(' ', '', paste("Crime_Data_2020/", i, "/NIBRS_VICTIM_OFFENDER_REL.csv")))
  victim_offender_rel <- rbind(victim_offender_rel, NIBRS_VICTIM_OFFENDER_REL)
}

victim_offender_rel <- victim_offender_rel[ , c("VICTIM_ID", "OFFENDER_ID",
                                                "RELATIONSHIP_ID")]
# rm(list= ls()[!(ls() %in% c('victims','offense','incidents','agency_list','victim_offender_rel'))])
```

#TODO
-Make two more chunks of 2018 and 2019 and use hella find & replace
-make Sure variable names are good. We may need to use new files instead

# Garbage Code
^Ignore this title it's referring to code that is commented out I chose to not knit
```{r,echo=FALSE}
# ##INCIDENTS
# # get a list of the folders in Crime_Data_NIBRS
# files <- list.files(path="CRIME_DATA_2020")
# #make empty data set for incident data
# incidents <- data.frame(matrix(ncol = 15, nrow = 0))
# names(incidents) <- names(NIBRS_incident)
# #go through each folder in Crime_Data_NIBRS and find corresponding incident 
# #table to bind it to incidents data frame
# for (i in files){
#   NIBRS_incident <- read_csv(gsub(' ', '', paste("Crime_Data_2020/", i, "/NIBRS_incident.csv")))
#   incidents <- rbind(incidents, NIBRS_incident)
# }
# #pull out unnecessary columns for incidents data set
# incidents <- incidents[ , c("DATA_YEAR", "AGENCY_ID", "INCIDENT_ID",
#                             "INCIDENT_DATE", "INCIDENT_HOUR")]
# ##VICTIMS
# victims <- data.frame(matrix(ncol = 16, nrow = 0))
# names(victims) <- names(NIBRS_VICTIM)  
# for (i in files){
#   NIBRS_VICTIM <- read_csv(gsub(' ', '', paste("Crime_Data_2020/", i, "/NIBRS_VICTIM.csv")))
#   victims <- rbind(victims, NIBRS_VICTIM)
# }
# victims <- victims[ , c("VICTIM_ID", "INCIDENT_ID", 
#                         "AGE_NUM", "SEX_CODE")]
# 
# ##AGENCY
# agency_list <- data.frame(matrix(ncol = 59, nrow = 0))
# names(agency_list) <- names(agencies)
# for (i in files){
#   agencies <- read_csv(gsub(' ', '', paste("Crime_Data_2020/", i, "/agencies.csv")))
#   agency_list <- rbind(agency_list, agencies)
# }
# agency_list <- agency_list[ , c("YEARLY_AGENCY_ID", "AGENCY_ID", "STATE_NAME", "STATE_ABBR",
#                                 "AGENCY_TYPE_NAME", "UCR_AGENCY_NAME", "COUNTY_NAME")]
# 
# ##OFFENDER
# offenders <- data.frame(matrix(ncol = 11, nrow = 0))
# names(offenders) <- names(NIBRS_OFFENDER)
# for (i in files){
#   NIBRS_OFFENDER <- read_csv(gsub(' ', '', paste("Crime_Data_2020/", i, "/NIBRS_OFFENDER.csv")))
#   offenders <- rbind(offenders, NIBRS_OFFENDER)
# }
# offenders <- offenders[ , c("OFFENDER_ID", "INCIDENT_ID")]
# 
# ##OFFENSE
# offense <- data.frame(matrix(ncol = 8, nrow = 0))
# names(offense) <- names(NIBRS_OFFENSE)
# for (i in files){
#   NIBRS_OFFENSE <- read_csv(gsub(' ', '', paste("Crime_Data_2020/", i, "/NIBRS_OFFENSE.csv")))
#   offense <- rbind(offense, NIBRS_OFFENSE)
# }
# offense <- offense[ , c("OFFENSE_ID", "INCIDENT_ID", 
#                         "OFFENSE_TYPE_ID", "LOCATION_ID")]
# 
# ##VICTIM OFFENDER REL
# victim_offender_rel <- data.frame(matrix(ncol = 5, nrow = 0))
# names(victim_offender_rel) <- names(NIBRS_VICTIM_OFFENDER_REL)
# for (i in files){
#   NIBRS_VICTIM_OFFENDER_REL <- read_csv(gsub(' ', '', paste("Crime_Data_2020/", i, "/NIBRS_VICTIM_OFFENDER_REL.csv")))
#   victim_offender_rel <- rbind(victim_offender_rel, NIBRS_VICTIM_OFFENDER_REL)
# }
# victim_offender_rel <- victim_offender_rel[ , c("VICTIM_ID", "OFFENDER_ID",
#                                                 "RELATIONSHIP_ID")]
# 
# rm(list= ls()[!(ls() %in% c('victims','offense','incidents','agency_list','victim_offender_rel'))])
# ```
# 
# # now we have incidents, victims, offenders, victim offender rel, and offense
# 
# # Merging Data
# ```{r}
# m1 <- left_join(victims, incidents, by = "INCIDENT_ID")
# m2 <- full_join(m1, offenders, by = "INCIDENT_ID")
# rm(m1)
# m3 <- left_join(m2, victim_offender_rel, by = c("VICTIM_ID", "OFFENDER_ID"))
# rm(m2)
# m4 <- left_join(m3, offense, by = "INCIDENT_ID")
# rm(m3)
# m5 <- left_join(m4, agency_list, by = "AGENCY_ID")
# rm(m4)
# m5 <- m5[ , c("DATA_YEAR.x", "COUNTY_NAME","AGENCY_ID", "STATE_ABBR", "INCIDENT_DATE",
#               "RELATIONSHIP_ID", "OFFENSE_TYPE_ID", "LOCATION_ID", "AGE_NUM")]
```

# Merging Data
```{r}
m1 <- left_join(victims, incidents, by = "INCIDENT_ID")
m2 <- full_join(m1, offenders, by = "INCIDENT_ID")
rm(m1)
m3 <- left_join(m2, victim_offender_rel, by = c("VICTIM_ID", "OFFENDER_ID"))
rm(m2)
m4 <- left_join(m3, offense, by = "INCIDENT_ID")
rm(m3)
m5 <- left_join(m4, agency_list, by = "AGENCY_ID")
rm(m4)
m5 <- m5[ ,c("DATA_YEAR", "COUNTY_NAME","AGENCY_ID",
             "STATE_ABBR", "INCIDENT_DATE",
              "RELATIONSHIP_ID", "OFFENSE_TYPE_ID", 
             "LOCATION_ID", "AGE_NUM")]
```

# Next Part
```{r}
# Clearing everything in my enviroment except the following... 
rm(list= ls()[!(ls() %in% c("m5","df"))])

set.seed(525)
df = slice_sample(m5,prop=0.1)
# rm(m5)
df <- df[ , c("DATA_YEAR", "COUNTY_NAME","AGENCY_ID",
              "STATE_ABBR", "INCIDENT_DATE",
              "RELATIONSHIP_ID", "OFFENSE_TYPE_ID", 
              "LOCATION_ID", "AGE_NUM")]
# make another data set filtering out anything not relating to property crime
# df2 = df %>% na.omit(RELATIONSHIP_ID)

# Child Relationship
df$child_rel = ifelse(df$RELATIONSHIP_ID ==  4|
                      df$RELATIONSHIP_ID ==  5|
                      df$RELATIONSHIP_ID == 10|
                      df$RELATIONSHIP_ID == 20|
                      df$RELATIONSHIP_ID == 23, 1,0)

# Partner Relationship
df$partner_rel = ifelse(df$RELATIONSHIP_ID ==  3|
                        df$RELATIONSHIP_ID == 27|
                        df$RELATIONSHIP_ID == 12|
                        df$RELATIONSHIP_ID == 21|
                        df$RELATIONSHIP_ID == 26, 1,0)

# Property Relationship
df$property_rel = ifelse( df$RELATIONSHIP_ID ==  1|
                          df$RELATIONSHIP_ID ==  2|
                          df$RELATIONSHIP_ID ==  4|
                          df$RELATIONSHIP_ID ==  7|
                          df$RELATIONSHIP_ID ==  8|
                          df$RELATIONSHIP_ID ==  8|
                          df$RELATIONSHIP_ID ==  9|
                          df$RELATIONSHIP_ID == 14|
                          df$RELATIONSHIP_ID == 16|
                          df$RELATIONSHIP_ID == 18|
                          df$RELATIONSHIP_ID == 24, 1,0)

# Stranger Relationship
df$stranger_rel = ifelse( df$RELATIONSHIP_ID ==  1|
                          df$RELATIONSHIP_ID ==  2|
                          df$RELATIONSHIP_ID ==  7|
                          df$RELATIONSHIP_ID ==  8|
                          df$RELATIONSHIP_ID ==  8|
                          df$RELATIONSHIP_ID ==  9|
                          df$RELATIONSHIP_ID == 14|
                          df$RELATIONSHIP_ID == 16|
                          df$RELATIONSHIP_ID == 18|
                          df$RELATIONSHIP_ID == 24|
                          df$RELATIONSHIP_ID == 25, 1,0)
# Burglary at home part
df$burglary_home_stranger = ifelse(df$RELATIONSHIP_ID == 24 &
                                   df$OFFENSE_TYPE_ID == 49 &
                                   df$LOCATION_ID == 20, 1, 0)

# Crimes against children
df$child_crime = ifelse(
        df$child_rel == 1 &
        df$OFFENSE_TYPE_ID == 51| # Simple Assault 
        df$OFFENSE_TYPE_ID == 56| # Fondling
        df$OFFENSE_TYPE_ID == 36| # Rape
        df$OFFENSE_TYPE_ID ==  1| # Homicide  
        # df$OFFENSE_TYPE_ID ==  3| # Statutory Rape
        df$OFFENSE_TYPE_ID ==  4| # Sexual Assault With An Object
        # df$OFFENSE_TYPE_ID ==  6| # Family Offenses, Nonviolent
        df$OFFENSE_TYPE_ID == 15| # Assisting or Promoting Prostitution
        # df$OFFENSE_TYPE_ID == 19| # Run Away
        df$OFFENSE_TYPE_ID == 19| # Runaway
        df$OFFENSE_TYPE_ID == 27| # Aggravated Assault
        df$OFFENSE_TYPE_ID == 29| # Kidnapping/Abduction
        df$RELATIONSHIP_ID == 30| # Prostitution Offenses
        df$OFFENSE_TYPE_ID == 32| # Murder and Nonnegligent Manslaughter
        df$OFFENSE_TYPE_ID == 38| # Negligent Manslaughter 
        df$OFFENSE_TYPE_ID == 43| # Sodomy
        df$OFFENSE_TYPE_ID == 44| # Intimidation
        df$OFFENSE_TYPE_ID == 55| # Incest
        df$OFFENSE_TYPE_ID == 59| # Human Trafficking, Commercial Sex Acts
        df$OFFENSE_TYPE_ID == 60,1, 0) # Human Trafficking, Involuntary Servitude

# Crimes against partners
df$partner_crime = ifelse(
        df$partner_rel == 1 &
        df$OFFENSE_TYPE_ID == 51| # Simple Assault 
        df$OFFENSE_TYPE_ID == 56| # Fondling
        df$OFFENSE_TYPE_ID == 36| # Rape
        df$OFFENSE_TYPE_ID ==  1| # Homicide  
        # df$OFFENSE_TYPE_ID ==  3| # Statutory Rape
        df$OFFENSE_TYPE_ID ==  4| # Sexual Assault With An Object
        # df$OFFENSE_TYPE_ID ==  6| # Family Offenses, Nonviolent
        df$OFFENSE_TYPE_ID == 15| # Assisting or Promoting Prostitution
        # df$OFFENSE_TYPE_ID == 19| # Run Away
        df$OFFENSE_TYPE_ID == 19| # Runaway
        df$OFFENSE_TYPE_ID == 27| # Aggravated Assault
        df$OFFENSE_TYPE_ID == 29| # Kidnapping/Abduction
        df$RELATIONSHIP_ID == 30| # Prostitution Offenses
        df$OFFENSE_TYPE_ID == 32| # Murder and Nonnegligent Manslaughter
        df$OFFENSE_TYPE_ID == 38| # Negligent Manslaughter 
        df$OFFENSE_TYPE_ID == 43| # Sodomy
        df$OFFENSE_TYPE_ID == 59| # Human Trafficking, Commercial Sex Acts
        df$OFFENSE_TYPE_ID == 60,1, 0) # Human Trafficking, Involuntary Servitude


# Crimes against strangers
df$stranger_crime = ifelse(
        df$stranger_rel == 1 &
        df$OFFENSE_TYPE_ID == 51| # Simple Assault 
        df$OFFENSE_TYPE_ID == 56| # Fondling
        df$OFFENSE_TYPE_ID == 36| # Rape
        df$OFFENSE_TYPE_ID ==  1| # Homicide  
        # df$OFFENSE_TYPE_ID ==  3| # Statutory Rape
        df$OFFENSE_TYPE_ID ==  4| # Sexual Assault With An Object
        # df$OFFENSE_TYPE_ID ==  6| # Family Offenses, Nonviolent
        # df$OFFENSE_TYPE_ID == 19| # Run Away
        df$OFFENSE_TYPE_ID == 19| # Runaway
        df$OFFENSE_TYPE_ID == 27| # Aggravated Assault
        df$RELATIONSHIP_ID == 30| # Prostitution Offenses
        df$OFFENSE_TYPE_ID == 32| # Murder and Nonnegligent Manslaughter
        df$OFFENSE_TYPE_ID == 38| # Negligent Manslaughter 
        df$OFFENSE_TYPE_ID == 55| # Incest
        df$OFFENSE_TYPE_ID == 59| # Human Trafficking, Commercial Sex Acts
        df$OFFENSE_TYPE_ID == 60,1, 0) # Human Trafficking, Involuntary Servitude



#dropping relationship columns
df = select(df, -c(child_rel,
                   partner_rel,
                   property_rel,
                   stranger_rel)) 

# sum(is.na(df$partner_crime))
df = mutate_at(df, c("partner_crime",
                     "child_crime",
                     "stranger_crime",
                     "burglary_home_stranger"), ~replace(., is.na(.), 0))

```

# Garbage Code
^Ignore this title it's referring to code that is commented out I chose to not knit
```{r, echo=FALSE}
# set.seed(525)
# all = m5 %>% sample_frac(0.1)
# # rm(m5)
# all <- all[ , c("DATA_YEAR", "COUNTY_NAME","AGENCY_ID", "STATE_ABBR", "INCIDENT_DATE",
#               "RELATIONSHIP_ID", "OFFENSE_TYPE_ID", "LOCATION_ID", "AGE_NUM")]
# # make another data set filtering out anything not relating to property crime
# 
# prop = all %>% na.omit(RELATIONSHIP_ID)
# pers = setdiff(all,prop)
# identical((sum(nrow(pers),nrow(prop))),nrow(all)) #hm should be true smh
# 
# pers$RELATIONSHIP_ID
```

# Making Combo Column
```{r}
#DROPPING NA COUNTIES
sum(is.na(df$COUNTY_NAME))
df = df %>% drop_na(COUNTY_NAME)

df =separate(
    data = df,
    col = COUNTY_NAME,
    sep = "; ",
    into = 
      c("county_1", 
        "county_2", 
        "county_3", 
        "county_4",
        "county_5"),
    remove = FALSE)


#DROPPING ALL obs. with >1 County
df = select(df, -c( county_2, 
                    county_3, 
                    county_4,
                    county_5)) 


df$MONTH = gsub("[^a-zA-Z]", "", df$INCIDENT_DATE)

df$MONTH = ifelse(df$MONTH == "JAN",1,
           ifelse(df$MONTH == "FEB",2,
           ifelse(df$MONTH == "MAR",3,
           ifelse(df$MONTH == "APR",4,
           ifelse(df$MONTH == "MAY",5,
           ifelse(df$MONTH == "JUN",6,
           ifelse(df$MONTH == "JUL",7,
           ifelse(df$MONTH == "AUG",8,
           ifelse(df$MONTH == "SEP",9,
           ifelse(df$MONTH == "OCT",10,
           ifelse(df$MONTH == "NOV",11,12)))))))))))

df$combo = str_c(df$county_1,"-",
                 df$STATE_ABBR,"-",
                 df$DATA_YEAR, "-",
                 df$MONTH)
df = df %>% 
  group_by(combo) %>% 
  summarise(partner_crime = sum(partner_crime),
            child_crime = sum(child_crime),
            stranger_crime = sum(stranger_crime),
            burglary_home_stranger = sum(burglary_home_stranger))


```



# Summary Stats
```{r}
skim(df)
```


Reading in other Data
```{r}
sc = read.csv("school_closure_data1.csv")
sc = sc %>% filter(year < 2021)
sc = select(sc, -c( X,statefips,
                    countyfips,
                    countyfips2,
                    countyfips3,
                    year,
                    state_abb,
                    county_name)) 
new = merge(sc,df, by = "combo")
new = new %>% 
      mutate(stud_per_school = total_students/number_schools) %>% 
      mutate(closed25 = 0.25 * (share_all_closed_25*total_students)) %>% 
      mutate(closed50 = 0.5  * (share_all_closed_50*total_students)) %>% 
      mutate(closed75 = 0.75 * (share_all_closed_75*total_students)) %>% 
      mutate(students_home = (closed25 + closed50 + closed75))

```


# First Regression
```{r}
reg1 = lm(child_crime~students_home, data = new)
# reported crime / total students~ percent student home +grandparents
# tidy(reg1)
summary(reg1)
reg2 = lm(partner_crime~students_home, data = new)
tidy(reg2)
# summary(reg2)
```












